An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
update learner

\begin{algorithm}
\caption{Construct Rules}
\label{alg:crules}
  \begin{algorithmic}[1]
  \State \textbf{constructRules}($e, \tau, S$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace type $\tau$\\
     \qquad \enspace \enspace set of entries $S$\\
     $R = \{\}$
     \For{each $t \in templates(\tau)$}
        \State Let $n$ be the arity of $t$
        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
        \For{each $p \in P$}
         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
           \For{$i = 1:n$}
           \State Create a $n$-tuple by placing $e$ at the $i$-th place and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
           \State $r = \textrm{constructRule}(u)$ 
            \If{$r$ is satisfied}
              $R = R \cup r$
            \EndIf
          \EndFor
        \EndFor
     \EndFor
     \State return $R$
  \end{algorithmic}
\end{algorithm}

@@

%this approach can be defined in Algorithm~\ref{alg:crules}.

%More formally, this approach can be defined in Algorithm~\ref{alg:plearn}. 
Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm~\ref{alg:plearn} only considers
templates without mixed types; that is, the arguments of the template are all similarly typed. Adding support for
mixed types is not much more difficult.

@@

>>>>

\begin{algorithm}
\caption{Construct Rules}
\label{alg:crules}
  \begin{algorithmic}[1]
  \State \textbf{constructRules}($e, \tau, S$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace type $\tau$\\
     \qquad \enspace \enspace set of entries $S$\\
     $R = \{\}$
     \For{each $t \in templates(\tau)$}
        \State Let $n$ be the arity of $t$.
        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
        \For{each $p \in P$}
         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
           \For{$i = 1:n$}
           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
           \State $r = \textrm{constructRule}(u)$ 
            \If{$r$ is satisfied}
              $R = R \cup r$
            \EndIf
          \EndFor
        \EndFor
     \EndFor
     \State return $R$
  \end{algorithmic}
\end{algorithm}

@@

Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm 1 only considers
templates without mixed types; that is, the arguments of the template are all of the same type. This is
demonstrated via the filtration step, which filters rules in a file that are possibly of the same type.  
Adding support for mixed types would be handled in a branching statement in Algorithm 1.
Note that in Algorithm~\ref{alg:crules}, constructRule refers to the creation of a rule from a tuple of entries, $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
Then the rule creation is formally represented as $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$; in order to 
determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated.

@@

\jon{I will include examples for things like mixed type, rule creation, etc after the translation section is finished.}
